%!TEX root = main.tex
\section{LDA} \label{sec:prob3}
In this section, we use latent Dirichlet allocation (LDA) to perform topic modeling on a corpus of text.

\subsection{Part 1}
The first part is very straightforward.
We installed the Mallet implementation of LDA and ran it on the corpus of text of 19,997 news articles in 20 categories from the Usenet newsgroups dataset.

\subsection{Part 2}
During training, we asked the model to discover 100 topics, which include several keywords related to the topic.
Two example topics are:
\begin{itemize}
	\item health cancer disease medical aids hiv number research patients page april volume newsletter study hicnet drug children risk years age 
	\item image data graphics package images program processing line format ray code objects analysis points center it's postscript sgi formats ftp
\end{itemize}
The first topic seems to be related to medicine/health and the second is related to image processing/computers.
The topics aren't extremely specific, but each component seems roughly connected.
However, if a human were to develop a list of keywords related to health, it probably would not include words like ``newsletter'' or ``april'', so there are some strange components of the topic lists.

Of the 20 article categories, we chose to analyze two in more detail: ``sci.med'' and ``rec.sport.hockey'', which include articles about Medicine and Hockey, respectively.
The top topics related to Medicine were:
\begin{enumerate}
	\item article pain doctor writes gordon banks patients good surgery treatment disease patient medicine blood intellect chronic skepticism surrender shameful chastity
	\item food msg eat diet article people fat writes foods chinese body eating effects taste reaction i'm effect apr steve meat
	\item candida yeast medical patients medicine symptoms treatment infection quack infections body steve doctors article clinical disease writes studies nutrition jon
\end{enumerate}
and the top topics related to Hockey were:
\begin{enumerate}
	\item period game play goal pts power shots puck blues goals flyers leafs team detroit win wings scoring penalty season goalie
	\item game games team win espn won year lost baseball fans boston division series hockey teams chicago pittsburgh fan season cubs
	\item team game players hockey writes play player article roger games apr league baseball good time year teams bob nhl ice 
\end{enumerate}
At first glance, these topics seem appropriate for the categories.
Medicine's top topics roughly relate to medicine, nutrition, and disease, whereas hockey's top topics include rules of the game and team names.
Upon closer look, there are some bizarre elements of the chosen topics, like ``i'm'' and ``jon'' for medicine, and ``bob'' and ``apr'' for hockey.
But, of the 60 keywords for hockey, only about 3 of them are ridiculous whereas the other 57 are very ``on-topic.''

\subsection{Part 3}
Then, we lowered the number of topics down to 20.
We hypothesized that this would lead to broader topics, because the same number of articles and words now would need to be binned into a smaller number of categories.
Interestingly, the number of article classes is now equal to the number of topics.

The first two resulting topics were:
\begin{itemize}
	\item writes article people don't objective moral truth true question evidence god point good i'm morality it's religion exist claim reason
	\item israel president jews israeli writes jewish war article people arab state peace stephanopoulos arabs world policy land years country american
\end{itemize}
These topics seem slightly more broad than before, but it's hard to measure this concept.

The top topics related to Medicine were:
\begin{enumerate}
	\item article medical writes disease study health patients food cancer number treatment men msg medicine research doctor sex drug aids studies
	\item don't it's people i'm good make time writes article that's i've things thing can't doesn't lot point you're find work
	\item writes article theory science fact universe evolution bill book university black water time don't apr michael physical scientific hole books
\end{enumerate}
and the top topics related to Hockey were:
\begin{enumerate}
	\item game team year games writes players article play hockey season baseball win good league player apr teams hit fans time
	\item don't it's people i'm good make time writes article that's i've things thing can't doesn't lot point you're find work
	\item san period convention pit party institute pts political adl det van april bos cal los committee college state vote karl 
\end{enumerate}
The first topic for each article category still seems appropriate, but the second and third are not very related.
This result matches with our original intuition that that there would be less specific topics to pair with each article type.